---
title: "Seminar Study 1a"
output: html_document
date: "2024-11-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Chi-squared power calculation


```{r cars}
library(pwr)
pwr.chisq.test(w = 0.27, N = NULL, df = 1, sig.level = .05, power = .8)
```

## Loading data CSV

```{r pressure, echo=FALSE}
# Get the current working directory
current_directory <- getwd()
file_name = "Dataset_S1A.csv"
# Get the absolute path of a file or directory
relative_path <- paste(current_directory, file_name, sep = "/")
absolute_path <- normalizePath(relative_path)
```


## Data Info

Gender (
  1 = female 
  2 = male
  )
  
  Age
  
Condition (
  0 = Observer perspective condition
  1 = Employee perspective condition
  )
  
Preferences_human_versus_robotic_replacement (
  1 = Preference human replacement
  2 = Preference robotic replacement
  )
  
Attention_check (
  1 = failed
  2 = passed
  3 = failed
  )
  
Qualitative_question

Education (
  1 = Less than high school
  2 = High School
  3 = Some college, no degree
  4 = Bachelor/Master`s degree
  5 = Doctoral degree
  6 = Other
  )
  
Occupation (
  1 = Legislators, senior officias and managers
  2 = Professionals or Technicians
  3 = Clerks
  4 = Service workers and shop and market sales workers
  5 = Skilled agricultural and fishery workers
  6 = Craft and related trades workers
  7 = Plant and machine operators and assemblers
  8 = Elementary occupations
  9 = Armed forced
  10 = Other
  )
  
Income (
  1 = Below $20,000 
  2 = $20,000 - $29,999
  3 = $30,000 - $39,999 
  4 = $40,000 - $49,999 
  5 = $50,000 or more
  )



## Set up variables

```{r pressure, echo=FALSE}

df <- read.csv(absolute_path, sep = ";")

# Display the first few rows of the data frame
condition <- df['Condition']
preferences <- df['Preferences_human_versus_robotic_replacement']
attention_check <- df['Attention_check']


```
# Data analysis

## Z-SCORE

```{r pressure, echo=FALSE}


# Observer Perspective (human vs robots)

condition_observer_worker <- 0                            # (0 == observer and 1 == worker )
n_human <- sum(condition == condition_observer_worker & 
                 preferences == 1 & attention_check == 2) # Number preferring human replacement
n_robot <- sum(condition == condition_observer_worker & 
                 preferences == 2 & attention_check == 2) # Number preferring robot replacement
total <- n_human + n_robot                                # Total sample size


# Proportion test with the null hypothesis that both groups are equally preferred (p = 0.5)

binom_test <- binom.test(n_human,                   
                         total, 
                         p = 0.5, 
                         alternative = "two.sided",
                         conf.level = 0.95)                         
                                                                        
# Z-score

p_hat <- n_human / total                                        # Observed proportion
p0 <- 0.5                                                       # Null hypothesis proportion
z_score <- (p_hat - p0) / sqrt((p0 * (1 - p0)) / n_observer)    # Compute the Z-score


# Compute Cohen's h

p1 <-  as.numeric(binom_test$estimate)                          # Proportion preferring human replacement
p2 <- 0.5                                                       # Null proportion
cohen_h <- 2 * (asin(sqrt(p1)) - asin(sqrt(p2)))


conf_interval <- binom_test$conf.int
conf_interval_string <- paste("95% CI: (",round(conf_interval[1], 3),",",round(conf_interval[2],3),")")
formatted_string_z <- sprintf("[%.2f%% versus %.2f%%; Z = %.4f; p = %.2f; %s ; Cohen_h: %.2f]",
                            (p1*100), (1-p1)*100,z_score, binom_test$p.value ,conf_interval_string, cohen_h)
result_z_score <- function(p)
if (p< 0.05){
  result_z <- sprintf("%.2f < 0.05 -> Reject H0, both proportions are different",p)
} else{
  result_z <- sprintf("%.2f > 0.05 ->  Not Reject H0, both proportions are equal",p)
}

```


## CHI-SQAURE

```{r pressure, echo=FALSE}


# Observed counts

observer_human <- sum(condition == 0 & preferences == 1 & attention_check == 2) # Participants in observer condition preferring human replacement
observer_robot <- sum(condition == 0 & preferences == 2 & attention_check == 2) # Participants in observer condition preferring robot replacement
employee_human <- sum(condition == 1 & preferences == 1 & attention_check == 2) # Participants in employee condition preferring human replacement
employee_robot <- sum(condition == 1 & preferences == 2 & attention_check == 2) # Participants in employee condition preferring robot replacement
total_human <- observer_human + employee_human
total_robot <- observer_robot + employee_robot

# Create the contingency table

data <- matrix(c(observer_human, observer_robot, 
                 employee_human, employee_robot), 
               nrow = 2, byrow = TRUE)
rownames(data) <- c("Observer", "Employee")
colnames(data) <- c("Human", "Robot")

chi_square_test <- chisq.test(data, correct=FALSE) # Perform chi-square test


# Confidential Interval

prop_test <- prop.test(c(observer_human, observer_robot), c(total_human,total_robot), correct=FALSE)
conf_interval <- prop_test$conf.int
conf_interval_string <- paste("95% CI: (",round(conf_interval[1], 3),",",round(conf_interval[2],3),")")

# Parameters for Cramér's V

n <- sum(data)                                 # Total number of observations
min_dim <- min(dim(data))       # Minimum dimension of the table
chi_square_value <- chi_square_test$statistic  # Chi-square statistic

cramers_v <- function(chi_square, n, min_dim) { # Function to calculate Cramér's V
  sqrt(chi_square / (n * (min_dim - 1)))
}


cramers_v_value <- cramers_v(chi_square_value, n, min_dim) # Calculate Cramér's V



formatted_string_chi <- sprintf("[X-squared(%s) = %.2f; p= %.2f; %s; Cramer's V = %.2f]",chi_square_test$parameter,chi_square_value,chi_square_test$p.value,conf_interval_string,cramers_v_value)
result_chi <- function(p)
if (p< 0.05){
  result_z <- sprintf("%.2f < 0.05 -> Reject H0",p)
} else{
  result_z <- sprintf("%.2f > 0.05 ->  Not Reject H0",p)
}

```



## LOGISSTIC REGRESION

```{r pressure, echo=FALSE}
# Step 1: Create the dataset
# Perspective: 0 = Observer, 1 = Employee
# Preference: 1 = Human replacement, 2 = Robot replacement

new_df <- df[, c("Condition", "Preferences_human_versus_robotic_replacement","Attention_check")]
filtered_df <- new_df[new_df$Attention_check == 2, ]

# Step 2: Combine the data into a data frame
data <- data.frame(perspective = filtered_df$Condition, preference = filtered_df$Preferences_human_versus_robotic_replacement)

# Convert 'preference' to a factor
data$preference <- factor(data$preference, levels = c(1, 2), labels = c("Human", "Robot"))

# Convert 'perspective' to a factor
data$perspective <- factor(data$perspective, levels = c(0, 1), labels = c("Observer", "Employee"))

# Step 3: Run the logistic regression model
# Logistic regression model predicting preference based on perspective
logistic_model <- glm(preference ~ perspective, data = data, family = binomial)

# Step 4: Calculate the Odds Ratio (exp(coefficient)) for interpretation
odds_ratio <- exp(coef(logistic_model))

# Step 5: Calculate and display the 95% Confidence Interval for the coefficient
confint_values_logistic <- confint(logistic_model)  # Get confidence intervals for the coefficients
conf_interval_logistic_regression_string <- paste("95% CI: (",round(confint_values_logistic[2,1], 3),",",round(confint_values_logistic[2,2],3),")")


# Step 6: Extract the Z-value (Wald statistic) and P-value from the summary output
z_value <- coef(summary(logistic_model))["perspectiveEmployee", "z value"]
p_value <- coef(summary(logistic_model))["perspectiveEmployee", "Pr(>|z|)"]

formatted_logistic_regression <- sprintf("[b=%.2f; Z= %.2f; p= %.2f; %s]",logistic_model$coefficients["perspectiveEmployee"], z_value, p_value,conf_interval_logistic_regression_string)

```


## Results

```{r pressure, echo=FALSE}
cat('\t\t\t----------------------------------\n')
cat('\t\t\t|  Z-Score Observer perspective. |\n')
cat('\t\t\t----------------------------------\n')
cat('*',formatted_string_z,'\n')
cat('*',result_z_score(binom_test$p.value),'\n\n')
cat('|---------------------------------------------------------------------------------------------|\n\n')

cat('\t\t\t----------------------------------\n')
cat("\t\t\t|         Chi-square Analysis    |\n")
cat('\t\t\t----------------------------------\n')
cat('*',formatted_string_chi,'\n')
cat('*',result_chi(chi_square_test$p.value),'\n\n')
cat('|---------------------------------------------------------------------------------------------|\n\n')

cat('\t\t\t ----------------------------------\n')
cat('\t\t\t|        Logistic Regression       |\n')
cat('\t\t\t ----------------------------------\n')
cat('*',formatted_logistic_regression,'\n\n')
cat('\tSummary logistic regression\n')
summary(logistic_model)
cat(' \tOdds ration \n\n')
odds_ratio
cat('|---------------------------------------------------------------------------------------------|\n\n')
```



